My title

### 2024-11-04 paper/paper.qmd
updated paper

```
The regression coefficients for the logistic and linear models are presented in the Appendix because they are not the outcome of interest. Please view @tbl-coe1 to @tbl-coe7.

@@

@@

```{r}
#| label: tbl-coe1
#| fig-cap: Logistic Regression Coefficients for Pennsylvania
#| echo: false
#| message: false
#| warning: false
# Tidy the logistic regression model
tidy_Pennsylvania <- tidy(logistic_Pennsylvania)

# Display the table using knitr::kable
kable(tidy_Pennsylvania, digits = 2, 
      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"))

```
```{r}
#| label: tbl-coe2
#| fig-cap: Logistic Regression Coefficients for Georgia
#| echo: false
#| message: false
#| warning: false
# Tidy the logistic regression model
tidy_Georgia <- tidy(logistic_Georgia)

# Display the table using knitr::kable
kable(tidy_Georgia, digits = 2, 
      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"))

@@

```{r}
#| label: tbl-coe3
#| fig-cap: Logistic Regression Coefficients for Michigan
#| echo: false
#| message: false
#| warning: false
# Tidy the logistic regression model
tidy_Michigan <- tidy(logistic_Michigan)

# Display the table using knitr::kable
kable(tidy_Michigan, digits = 2, 
      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"))

@@

```{r}
#| label: tbl-coe4
#| fig-cap: Logistic Regression Coefficients for North_Carolina
#| echo: false
#| message: false
#| warning: false
# Tidy the logistic regression model
tidy_North_Carolina <- tidy(logistic_North_Carolina)

# Display the table using knitr::kable
kable(tidy_North_Carolina, digits = 2, 
      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"))

@@

```{r}
#| label: tbl-coe5
#| fig-cap: Logistic Regression Coefficients for Arizona
#| echo: false
#| message: false
#| warning: false
# Tidy the logistic regression model
tidy_Arizona <- tidy(logistic_Arizona)

# Display the table using knitr::kable
kable(tidy_Arizona, digits = 2, 
      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"))

@@

```{r}
#| label: tbl-coe6
#| fig-cap: Logistic Regression Coefficients for Wisconsin
#| echo: false
#| message: false
#| warning: false
# Tidy the logistic regression model
tidy_Wisconsin <- tidy(logistic_Wisconsin)

# Display the table using knitr::kable
kable(tidy_Wisconsin, digits = 2, 
      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"))

```{r}
#| label: tbl-coe7
#| fig-cap: Logistic Regression Coefficients for Nevada
#| echo: false
#| message: false
#| warning: false
# Tidy the logistic regression model
tidy_Nevada <- tidy(logistic_Nevada)

# Display the table using knitr::kable
kable(tidy_Nevada, digits = 2, 
      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"))

>>>>

```
The regression coefficients for the logistic and linear models are presented in the Appendix because they are not the outcome of interest.

@@

```
\FloatBarrier

```{r}
#| echo: false
#| message: false
#| warning: false
# Tidy the logistic regression model
tidy_Pennsylvania <- tidy(logistic_Pennsylvania)

# Display the table using knitr::kable
kable(tidy_Pennsylvania, digits = 2, 
      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"),
      caption = "Logistic Regression Coefficients for Pennsylvania")

```
```{r}
#| echo: false
#| message: false
#| warning: false
# Tidy the logistic regression model
tidy_Georgia <- tidy(logistic_Georgia)

# Display the table using knitr::kable
kable(tidy_Georgia, digits = 2, 
      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"),
      caption = "Logistic Regression Coefficients for Georgia")

@@

```{r}
#| echo: false
#| message: false
#| warning: false
# Tidy the logistic regression model
tidy_Michigan <- tidy(logistic_Michigan)

# Display the table using knitr::kable
kable(tidy_Michigan, digits = 2, 
      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"),
      caption = "Logistic Regression Coefficients for Michigan")

@@

```{r}
#| echo: false
#| message: false
#| warning: false
# Tidy the logistic regression model
tidy_North_Carolina <- tidy(logistic_North_Carolina)

# Display the table using knitr::kable
kable(tidy_North_Carolina, digits = 2, 
      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"),
      caption = "Logistic Regression Coefficients for North_Carolina")

@@

```{r}
#| echo: false
#| message: false
#| warning: false
# Tidy the logistic regression model
tidy_Arizona <- tidy(logistic_Arizona)

# Display the table using knitr::kable
kable(tidy_Arizona, digits = 2, 
      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"),
      caption = "Logistic Regression Coefficients for Arizona")

@@

```{r}
#| echo: false
#| message: false
#| warning: false
# Tidy the logistic regression model
tidy_Wisconsin <- tidy(logistic_Wisconsin)

# Display the table using knitr::kable
kable(tidy_Wisconsin, digits = 2, 
      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"),
      caption = "Logistic Regression Coefficients for Wisconsin")

@@

```{r}
#| echo: false
#| message: false
#| warning: false
# Tidy the logistic regression model
tidy_Nevada <- tidy(logistic_Nevada)

# Display the table using knitr::kable
kable(tidy_Nevada, digits = 2, 
      col.names = c("Term", "Estimate", "Std. Error", "Statistic", "p-value"),
      caption = "Logistic Regression Coefficients for Nevada")
